Stochastic Variance-Reduced Policy Gradient

### 2018-02-08 svrpg.tex
version for first submission (minus todos)

\subsection{Zeroth update}
As noted in Section \ref{sec:alg}, the update performed at the beginning of each epoch is equivalent to a full-gradient update. In our setting, where collecting samples is particularly expensive, the $B$ trajectories collected using the snapshot trajectory $\pi_{\tilde{\vtheta}^s}$ feel like a waste of data. In practice, we just perform an approximate full gradient update using the $N$ trajectories sampled to compute $\gradApp{\tilde{\vtheta}^s}{N}$, \ie
\begin{align*}
	&\vtheta_{1}^{s+1} = \tilde{\vtheta}^s + \alpha\gradApp{\tilde{\vtheta}^s}{N} \\
	&\vtheta_{t+1}^{s+1} = \vtheta_t^{s+1} + \alpha v_t^{s+1} \text{ for $t=1,\dots,m-1$}.
\end{align*}
In the following, we will always assume this practical variant is employed.

@@

\paragraph{Cart-pole.} Figure \ref{fig:cartpole} compares SVRPG with G(PO)MDP on the continuous cart-pole balancing task. Here the performance gain is evident. Notice also how the variance of our algorithm is visibly smaller.

@@

\paragraph{Swimmer} The mujoco swimmer task is far more difficult than cart-pole. The longer horizon and the more complex dynamics can have a dangerous impact on the variance of importance weights. In this case, the self-normalization technique proposed in Section \ref{sec:selfnorm} brings an improvement, as shown in Figure \ref{fig:swimmertwo}. Although the confidence intervals are never disjoint, the average of the self-normalized version is always higher, which we consider enough to employ the variant in the subsequent comparison. Figure \ref{fig:swimmerone} shows self-normalized SVRPG against G(PO)MDP. On average, our algorithm dominates for almost the entire task. Toward the end of the task, the improvement becomes statistically significant. Also in this case, the different width of confidence intervals suggest that SVRPG is more robust, especially in the early iterations.

>>>>

\subsection{Zeroth Update}
As noted in Section \ref{sec:alg}, the update performed at the beginning of each epoch is equivalent to a full-gradient update. In our setting, where collecting samples is particularly expensive, the $B$ trajectories collected using the snapshot trajectory $\pi_{\tilde{\vtheta}^s}$ feel like a waste of data. In practice, we just perform an approximate full gradient update using the $N$ trajectories sampled to compute $\gradApp{\tilde{\vtheta}^s}{N}$, \ie
\begin{align*}
	&\vtheta_{1}^{s+1} = \tilde{\vtheta}^s + \alpha\gradApp{\tilde{\vtheta}^s}{N} \\
	&\vtheta_{t+1}^{s+1} = \vtheta_t^{s+1} + \alpha v_t^{s+1} \text{ for $t=1,\dots,m-1$}.
\end{align*}
In the following, we will always assume this practical variant is employed.

@@

\paragraph{Cart-pole.} Figure \ref{fig:cartpole} compares SVRPG with G(PO)MDP on the continuous cart-pole balancing task. Despite using more trajectories for each parameter, our algorithm shows faster convergence, which can be ascribed to the 
better quality of updates due to variance reduction.

@@

\paragraph{Swimmer} The mujoco swimmer task is far more difficult than cart-pole. The longer horizon and the more complex dynamics can have a dangerous impact on the variance of importance weights. In this case, the self-normalization technique proposed in Section \ref{sec:prac} brings an improvement, as shown in Figure \ref{fig:swimmertwo}. Although the confidence intervals are never disjoint, the average of the self-normalized version is always higher, which we consider enough to employ the variant in the next comparison. Figure \ref{fig:swimmerone} shows self-normalized SVRPG against G(PO)MDP. On average, our algorithm dominates for almost the entire task. Also here, we note an increase of speed in early iterations. Toward the end of the task, the improvement becomes statistically significant.
